\documentclass[12pt]{article}

\title{\vspace{-0.8in}Shao-En Chen}

\author{
	$(\texttt{+}886) 932322975$ $\bullet$ seanchen47@gmail.com
	\\https://github.com/ShaoEnChen
}
% omit date in \maketitle
\date{}

\linespread{1.2}
\setlength{\parindent}{0cm}

\usepackage{times}
\usepackage{nopageno}
\usepackage{geometry}
\geometry{a4paper,margin=0.8in}
\usepackage{enumitem}
\setenumerate{label=$\cdot$, leftmargin=*, itemsep=-0.3em, topsep=-0.6em}

\begin{document}

\maketitle

\textbf{\large{\uppercase{Education}}}
\hrulefill{}

	\vspace{0.5em}

	\textbf{National Taiwan University} \hfill Taipei, Taiwan

	Bachelor of Business Administration \hfill Sep. 2013 -- Jun. 2017

	\textbf{Department of Information Management}, GPA: 3.43 / 4.3

	\textbf{Relevant Courses}

	Data Structures, Algorithms, Operating Systems, Database Management, Programming Design, Information Security, Computer Networks and Applications, Calculus, 3D Creation In Reality, Information Architecture and Web Design, Introduction to Digital Speech Processing

	\vspace{1em}

\textbf{\large{\uppercase{Research Experience}}}
\hrulefill{}

	\vspace{0.5em}

	\textbf{Analysis of Health Seeking Behavior} \hfill Feb. 2016 -- Aug. 2016

	\textit{Advisor: Prof. Seng-Cho Chou, Assoc. Prof. Hsin-Min Lu \hfill National Taiwan University}

	\begin{enumerate}

		\item Classified and analyzed patients living in the twelve districts of Taipei under different factors to recognize the insights causing differences to their health seeking behaviors

		\item Implemented k-means algorithm and hierarchical clustering to process data from Taiwan government healthcare information resources

	\end{enumerate}

	\vspace{1em}

\textbf{\large{\uppercase{Work Experience}}}
\hrulefill{}

	\vspace{0.5em}

	\textbf{Stormed Inc.} \hfill Nov. 2015 -- Apr. 2016

	\textit{Quality Assurance \hfill Taipei, Taiwan}

	\begin{enumerate}

		\item Utilized test automation framework to simulate user behavior and tracked bugs to ensure that products ran smoothly and met demands

		\item Created detailed, comprehensive and well-structured test plans and test cases

	\end{enumerate}

	\vspace{0.5em}

	\textbf{Trisoap} \hfill Apr. 2016 -- Present

	\textit{Front-End Developer \hfill Taipei, Taiwan}

	\begin{enumerate}

		\item Designed and built company website, provided responsive and user-friendly web design, helped promote products effectively

		\item Monitored server activities to ensure normal service

		\item Will develop customer service chatbot on official site, Facebook messenger and LINE

	\end{enumerate}

	\vspace{0.5em}

	\textbf{Piece Work} \hfill Nov. 2016 -- Present

	\begin{enumerate}

		\item Built e-commerce websites

		\item Gained rich experience in website set up and server maintainance

	\end{enumerate}

	\vspace{1em}

\textbf{\large{\uppercase{Selected Term Projects}}}
\hrulefill{}

	\vspace{0.5em}

	\textbf{Graduation Project: Stock Market Simulator Web Game} \hfill Aug. 2016 -- Dec. 2016

	\textit{Advisor: Prof. Seng-Cho Chou \hfill National Taiwan University}

	\begin{enumerate}

		\item Built a website for clients to simulate stock trading and compete with others under Taiwan 50's real stock data

		\item Attended a FinTech competition and business model workshop held by FinTechBase

	\end{enumerate}

	\vspace{0.5em}

	\textbf{Information Architecture and Web Design} \hfill Feb. 2016 -- Jun. 2016

	\begin{enumerate}

		\item Designed in groups and built a user-friendly website with clear structure and information architecture for users to search for music and lyrics

		\item Won the second prize in twelve groups

	\end{enumerate}

	\vspace{0.5em}

	\textbf{Computer Networks and Applications} \hfill Sep. 2015 -- Jan. 2016

	\begin{enumerate}

		\item Built a P2P transaction system which could transfer money and provide immediate status and history records for each account under terminal, all transactions encrypted

	\end{enumerate}

	\vspace{1em}

\textbf{\large{\uppercase{Extracurricular}}}
\hrulefill{}

	\vspace{0.5em}

	\textbf{NTU Challenge} \hfill Jul. 2016 -- Apr. 2017

	\textit{Advisor: Taidah Entrepreneurship Center, D-School@NTU \hfill National Taiwan University}

	\begin{enumerate}

		\item Coordinated with 28 members and held an innovative entrepreneurship competition with 919 competitors and 212 teams attending

		\item Designed and built multiple websites and web applications for official website, user profiles, final summit conference and else

		\item Organized and participated offline events, including workshops, judging meetings, teams interview and competitors party

	\end{enumerate}

	\vspace{0.5em}

	\textbf{Practicode} \hfill May. 2017 -- Jul. 2017

	\begin{enumerate}

		\item Wrote technical blog posts and translated articles every two weeks on Medium

		\item Received the most page views and read ratio among the members

	\end{enumerate}

	\vspace{0.5em}

	\textbf{Side Projects} \hfill Oct. 2015 -- Present

	\begin{enumerate}

		\item Worked on side projects including web-based voting system and travel records

	\end{enumerate}

	\vspace{0.5em}

	\textbf{Design Kit: The Course for Human-Centered Design} \hfill May. 2016 -- Jul. 2017

	\begin{enumerate}

		\item Completed the 7-week course offered by Acumen and IDEO.org and learned about the methods and tools of human-centered design while tackling real-world design challenges, earned official statement of accomplishment

		\item Covered topics including research methods, concept generation, and rapidly prototyping

		\item Recognized the insights and worked on solutions to malnutrition of white-collar workers

	\end{enumerate}

	\vspace{0.5em}

	\textbf{HackNTU} \hfill Aug. 21st -- 23rd, 2015

	\begin{enumerate}

		\item Participated in hackathon in NTU and built a forum application prototype

		\item Users could raise questions and discuss about current events with information visualization

	\end{enumerate}

	\vspace{1em}

\textbf{\large{\uppercase{Technical Strengths}}}
\hrulefill{}

	\vspace{0.5em}

	\textbf{Programming Languages} \hfill C++, JavaScript, HTML, CSS, PHP, Java, Python, R

	\vspace{0.5em}

	\textbf{Toolkit} \hfill Design Thinking, LaTeX, GitHub

	\hfill JQuery, Vue.js, Django, Robot Framework, MySQL

	\hfill Linux, AWS, GCP

\end{document}
